\boldmath Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2021-06-14 authors_responses/first_tac_rejection/authors_response.tex
Author's response skeleton tex added, all editor and reviewer comments added just need to write their responses renamed the response file from final (name was copied when file was copied)

\title{\boldmath Cryptographically Privileged State Estimation With Gaussian Keystreams}
\subtitle{Response to Reviewers' Comments - Submission L-CSS 21-0154}
\author{Marko Ristic\and Benjamin Noack\and Uwe D. Hanebeck}

@@

Dear Dr. Ji-Feng Zhang,\\
Dear Reviewers,

We would like to thank you all for your responses and agreement on accepting our manuscript. As specified in the Author's Checklist, we list the changes made to the accepted manuscript here. The changes consist of switching to the final version template and minor wording and spelling changes. Throughout this response, reviewers' comments are in \reviewtext{blue}.

@@

\section*{Response to the Editor's Report}
\def\thesection{E}
\begin{rebuttal} %\setcounter{enumi}{-1}
\item \reviewtext{All the Reviewers are fine with the revised version. Accordingly, I am glad to recommend the paper publication.

One reviewer pointed out a possible small typo in a reference. I have checked that: the reference given by the authors is correct. I guess the reviewer found the draft of the book in http://staff.ustc.edu.cn/\\\~{}mfy/moderncrypto/reading\%20materials/Introduction\_to\_Modern\_Cryptography.pdf which does not correspond exactly with the published version.}

We are happy to hear of your decision, thank you. Regarding the reference, we have left it as it was submitted in the accepted version.

@@

\section*{Response to the Comments of Reviewer 1 (46379)}
\def\thesection{R1}
\begin{rebuttal}
\item \reviewtext{The authors have answered all my earlier concerns.}

We are glad to hear this, thank you.

@@

\section*{Response to the Comments of Reviewer 2 (46381)}
\def\thesection{R2}
\begin{rebuttal}
\item \reviewtext{The authors have addressed my comments}

We are happy we could address them all, thank you.

@@

\section*{Response to the Comments of Reviewer 3 (44309)}
\def\thesection{R3}
\begin{rebuttal}
\item \reviewtext{The reviewer only have the following one more suggestion.

1.Could the author explain more about the negligible function \textbackslash eta in Definition 2.3. and make a definition of this function in this paper? The reviewer cannot find the definition 3.4. in ref [8] which may be a different version.}

We're sorry to hear that the reference was not easier to find. The editor has indicated that the reference was correct and differs from the book draft that can be found online, so we have left it unchanged. We're glad we could address your remaining suggestions.

@@

%\includepdf[pages=-]{diff}

>>>>

\title{\boldmath Privacy-Preserving Localization Using Private Linear-Combination Aggregation}
\subtitle{Response to Reviewers' Comments - Submission IEEE-TAC 20-2108}
\author{Marko Ristic\and Benjamin Noack\and Uwe D. Hanebeck}

@@

Dear Dr. Zhiwei Gao,\\
Dear Reviewers,

We would like to thank you all for your thorough and helpful reviews. In this letter, we will describe how editor and reviewer comments, questions and suggestions have been addressed. Throughout this response, reviewers' comments are in \reviewtext{blue}.

@@

\section*{Response to the Editor's Report}
\def\thesection{E}
\begin{rebuttal} %\setcounter{enumi}{-1}
\item \reviewtext{Based on the reviews, it is our decision that the paper cannot be accepted for publication in the Transactions in its present form.}

Our response.

\item \reviewtext{The reviewers feel the paper interesting, which many include publishable materials. On the other hand, the reviewers feel the paper should be reorganized by shortening the length (e.g. introduction etc.), and highlight the novelty and contribution. Also the relevance of the paper to the journal should be clarified.}

Our response.

\item \reviewtext{We encourage you to examine carefully the comments of the enclosed reviews and to consider making a major revision of the paper, which can be resubmitted as a Technical Note, to the Transactions on Automatic Control.  If you do submit a revised version of the paper as a Technical Note, you should take care that the paper is reduced to no
more than 8 double-column pages using IEEE template.}

Our response.

\item \reviewtext{In your letter of transmittal, you should include a detailed "author's response" document describing the changes in the paper and you should refer to the present paper number.

Please login, click on the "Author" link at the bottom of your access page, and upload your technical note under the SAME reference number. A new reference number will be assigned to your revised paper.}

Our response.

@@

\section*{Response to the Comments of Reviewer 1 (222511)}
\def\thesection{R1}
\begin{rebuttal}
\item \reviewtext{This paper concerns the localization problem under privacy constraints. Cryptographic schemes have been devised by the authors to achieve some privacy requirements. The contribution is significant enough and the paper is well written but hard to understand for a usual reader of IEEE TAC due to sections with cryptographic background.}

Our response.

\item \reviewtext{As a TAC paper, performance analysis in terms of estimation accuracy was expected but is actually missing.}

Our response.

\item \reviewtext{This reviewer wonders if IEEE TAC is well adapted for an efficient exposition of the authors' findings.}

Our response.

\item \reviewtext{In the framework of a Control theory paper, cryptographic notions would be kept as minimum as possible in the main body of the paper or moved to Appendices.}

Our response.

@@

\section*{Response to the Comments of Reviewer 2 (222527)}
\def\thesection{R2}
\begin{rebuttal}
\item \reviewtext{This paper deals with a suitable notion of linear-combination aggregation encryption and provides a cryptographically secure instance applied to a filter with range-sensor measurements. This approach keeps navigator location, sensor's location and sensors' measurements private during navigation.

The proposed approach is interesting and the results are technically sound. The literature review is OK. But the organization of paper and its length make its reading difficult.}

Our response.

\item \reviewtext{The reviewer encourages the authors to reorganize the article by greatly shortening it and to highlight the novelty.}

Our response.

\item \reviewtext{Some additional comments are given below:

-Introduction (2 pages) is too long and does not focus on the main ideas of the paper. There are too many reminders of classical notions.}

Our response.

\item \reviewtext{-Equation (3): i from 1 to n must be added.}

Our response.

\item \reviewtext{-The actual computation steps are in fact scattered all over the paper, in several sections.  In the current version, the reader has to collect all the scattered pieces to come out with the approach. I would therefore, strongly recommend the authors to summarize all the steps of the approach gathered by the end of the paper, to help the reader directly use and implement the algorithm.}

Our response.

\item \reviewtext{-Page 10, Equation (36), Right part of Equation: d is from 0 to D}

Our response.

\item \reviewtext{-Inequality (50) must be clarified,}

Our response.

\item \reviewtext{-Algorithm 1, steps 2/3/4, it is F\_\{k-1\},}

Our response.

\item \reviewtext{-Section VIII-some explanations on the process model must be added. Figure 6 is too small; it is difficult to distinguish the different lines.}

Our response.

@@

\section*{Response to the Comments of Reviewer 3 (229727)}
\def\thesection{R3}
\begin{rebuttal}
\item \reviewtext{This paper presented a theoretical framework for privacy-preserving localisation combining the encryption scheme and filtering. In particular, the private linear-combination aggregation has been adopted in the presented framework. Basically, the contribution of the paper is clearly indicated with an interesting and important topic. However, some technical problems need to be further clarified. Therefore, a major revision is necessary in my opinion.}

Our response.

\item \reviewtext{1) Is any filtering method can be integrated into the presented framework? If so, can we replace the method via numerical approach such as particle filter.}

Our response.

\item \reviewtext{2) How does the linear combination reflect the dynamics of the investigated system in Eq.(2)?}

Our response.

\item \reviewtext{3) Why is the noise of the system Gaussian? In Eq.(2), function f() is known then what is the physical meaning of the Gaussian process noise?}

Our response.

\item \reviewtext{4) In the paper, the noise is depended on covariance matrix \$Q\$ which is also particularly used in Algroithm 1, however, in practice, Q is unmeasurable and unknown. How to estimate the value of Q in terms of performance guarantee.}

Our response.

\item \reviewtext{5) The experimental results are limited. The comparison is essential to validate the performance of the presented algorithm. What about using the existing filtering method to demonstrate the various encryption scheme?}

Our response.

\item \reviewtext{6) There are some typos in the manuscript please correct them, for example, page 1 Notation, '\$\textbackslash left\textbackslash\textbar\textbackslash underline a\textbackslash right\textbackslash\textbar\$ the vector norm' should be '\$\textbackslash left\textbackslash\textbar\textbackslash underline a\textbackslash right\textbackslash\textbar\$ is the vector norm' etc.}

Our response.

@@

% \includepdf[pages=-]{diff}
